Forecasting the 2024 US Presidential Election

### 2024-11-04 paper/paper.qmd
Updated models

Our primary objective was to clean, organize, and analyze U.S. presidential election polling data to provide insights into voter preferences by state. This involved selecting data from reputable pollsters, organizing it by state, and addressing any missing or incomplete entries. Additional datasets were merged where necessary, and after thoroughly addressing missing values, we finalized a polished dataset ready for analysis. Below is a table summarizing the polling data by state, showcasing voter preferences by party and demographic breakdowns. The table highlights key trends and differences across states in terms of party lean and demographic distribution. @fig-predictors-pct-summary-1 and @fig-predictors-pct-summary-2 provides a snapshot of these findings.

```{r}
#| label: fig-predictors-pct-summary
#| tbl-cap: "Latest Poll Points by Party"
#| echo: false
#| warning: false
#| message: false

@@

@@

@@

## Measurement  
We chose Emerson as our primary pollster, and the reasoning for this is detailed in @sec-appenA. Emerson's polls offered crucial information, such as polling dates, party affiliations, sample sizes, and the percentage of support for each political party.

@@

```{r}
#| label: tbl-final-summary
#| echo: false
#| warning: false
#| message: false
# Filter time_data for 'DEM' in the 'party' column
dem_data <- time_data %>%
  filter(party == "DEM")

@@

# Print the final summary table using kable
library(knitr)
kable(
  final_summary_table,
  caption = "Final Summary Table of 95% Confidence Intervals for Common States",
  col.names = c("State", "DEM Mean (%)", "DEM Lower 95%", "DEM Upper 95%", "REP Mean (%)", "REP Lower 95%", "REP Upper 95%"),
  format = "markdown"
)

@@

```{r}
#| label: fig-points-over-time
#| tbl-cap: "Parties Approval and Leaning Preferences"
#| echo: false
#| warning: false
#| message: false

@@

# Appendix {-}

>>>>

Our primary objective was to clean, organize, and analyze U.S. presidential election polling data to provide insights into voter preferences by state. This involved selecting data from reputable pollsters, organizing it by state, and addressing any missing or incomplete entries. Additional datasets were merged where necessary, and after thoroughly addressing missing values, we finalized a polished dataset ready for analysis. Below is a table summarizing the polling data by state, showcasing voter preferences by party and demographic breakdowns. The table highlights key trends and differences across states in terms of party lean and demographic distribution. @tbl-predictors-pct-summary-1 and @tbl-predictors-pct-summary-2 provides a snapshot of these findings.

```{r}
#| label: tbl-predictors-pct-summary-1
#| tbl-cap: "Voter Party Preferences by State"
#| echo: false
#| warning: false
#| message: false

@@

# Create summary table
poll_summary_party <- poll_summary %>%
  select(State, `Democrat Pct`, `Republican Pct`, `Voted Biden 2020`, `Voted Trump 2020`)

@@

```{r}
#| label: tbl-predictors-pct-summary-2
#| tbl-cap: "Demographic Breakdowns by State"
#| echo: false
#| warning: false
#| message: false

# Create summary table
poll_summary_demographics <- poll_summary %>%
  select(State, `High Educated`, `Low Educated`, `Female`, 
         `Male`, `Nonbinary`, `Caucasian`, `Minority Ethnicity`)

@@

## Measurement  
We chose Emerson as our primary pollster, and the reasoning for this is detailed in @sec-appendix. Emerson's polls offered crucial information, such as polling dates, party affiliations, sample sizes, and the percentage of support for each political party.

@@

```{r}
#| label: tbl-final-summary
#| tbl-cap: "Final Summary Table of 95% Confidence Intervals for Common States"
#| echo: false
#| warning: false
#| message: false
# Filter time_data for 'DEM' in the 'party' column
dem_data <- time_data %>%
  filter(party == "DEM")

@@

# Print the final summary table using kable
library(knitr)
kable(
  final_summary_table,
  col.names = c("State", "DEM Mean (%)", "DEM Lower 95%", "DEM Upper 95%", "REP Mean (%)", "REP Lower 95%", "REP Upper 95%"),
  format = "markdown"
)

@@

```{r}
#| label: fig-points-over-time
#| fig-cap: "Parties Approval and Leaning Preferences"
#| echo: false
#| warning: false
#| message: false

@@

# Appendix {#sec-appendix}
